### 2019-09-20 NA_paper/manuscript_II/NA_temp/qso_paperII.tex
Update paper and text

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses (\mbh) correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar). 
 %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently.
So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$). It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample by two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAMs). We adopt \hst\ to take images of the 32 AGNs in multi-bands and deriving the trustworthy stellar mass and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh. Taking the measurement uncertainty and selection bias into account, %by adopting the same selection function to choose the simulating sample,
we find that both models agree well with the data, in terms of the central distribution and scatters. Considering the two models use very different recipes, their agreements to the data indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process. The intrinsic scatter of our high-$z$ sample is close to simulations and local ones, which is against the central limit theorem. To some extend, our result attests that there is a physical connection induces an ordering so that the more massive black holes are linked to the more massive masses.

@@

% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
To extend the comparison to the simulation models to higher redshift, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}. The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming. We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 again, or cite to the QSO I paper?}. As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above the 0.1 to ensure the homogeneity.

@@

\begin{figure}[t]
\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions to put here.}
}
\label{fig:AGN_select}
\end{figure}

To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII) and semi-analytic models (SAM). These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively. The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details. On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems. However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as (SAM). 
MBII and SAM have made successful predictions in previous works \cite{Menci2014, Menci2016, Khandai2015}. We refer the interested readers to these works for more details.

%\section*{Results}
%Selection effect into account
We collect a sample of AGNs in the MBII simulation at $z=1.5$ and compare their scaling relations the observed ones. To take the measurement uncertainty and the selection effect into account, we inject the {\it random} noise to the simulated sample to mimic the scattering effect that caused by the uncertainty. The assumed uncertainty levels are comparable to the realistic, which are $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively. We then select the sample that falls into the selection window, as shown in Figure~\ref{fig:selectfunc}. We investigated the predicted scaling relations by the MBII, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}. From a quick glimpse, one can see that the samples are overlapped with each other, showing an agreement between the predicted scaling relations and observations. To quantify this agreement, we perform the linear fitting to the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval. We then use the same slope value to obtain the best-fit result for the observed sample. We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical ($0.06$~dex mismatch). For the \mbh-\mstar relations, the mismatch ($0.15$~dex) is small and within 1$-\sigma$ level. We compare how the sample scatter to its central line and find that the simulations and the observations demonstrate a significant similarity. Given that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations to be at the same level, which it $0.25$~dex (see method section for details).

\begin{figure}[t]
\includegraphics[width=1.0\linewidth]{MBII_selectfunc.pdf}
\caption{The selection window as adopted for selecting the MBII simulated sample. The yellow background clouds shows the overall sample at $z=1.5$. We add the random uncertainty to the simulation and select the ones located in the selection window (i.e. red region). The green sample are the high-$z$ sample.}
\label{fig:selectfunc}
\end{figure}
%comparison to simulation (flux ratio also)

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.5\linewidth]{MBII_ML.pdf} &
\includegraphics[width=0.5\linewidth]{MBII_MM.pdf} \\
\end{tabular}
\caption{
Comparing the scaling relations between the observed scaling relations to the predicted samples by the MBII simulation. In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation, respectively. The blue grids are the overall galaxies that predicted in the MBII simulation and the red ones are selection effect considered. We red line shows the best-fit linear relations for the simulated selected sample. We fix the slope value to fit for the observed sample and find that the mismatch of the interceptions are within $1-\sigma$ difference for both relations. %{\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
}
\label{fig:MBII_comp}
\end{figure*}

The comparisons between the observed scaling relations to the SAM model are presented in Figure~\ref{fig:SAM_comp}. Rather than predict each individual simulated sample, the SAM model describes the possibility clouds to demonstrate the density distribution of the scaling relations. We use two sets of color contours to demonstrate the possibility distribution at $z=1.5$ epoch, before and after adopting the selection window. The comparisons show great consistency that the hot zones in the SAM {\it selection-effect-considered} contours at $\log($\mbh$)~\in[7.5, 8.56]$ are well matched to the observed relations. We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one. \ding{To be updated with Nicola's data.}

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 24mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
\includegraphics[trim = 30.5mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
\end{tabular}
\caption{ Similar to the Figure~\ref{fig:MBII_comp}, we compare the observation to the SAM models. The blue background contours show the overall sample distribution and the red ones are the relations after considering the selecting effect. We see that the yellow contours are well matched to the hot zones for the red contours.
}
\label{fig:SAM_comp}
\end{figure*}

To help understand if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples. For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3. For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band. We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other. The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively. We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively. \ding{more interpretations needs to put here}.

@@

Without any physical mechanisms, the central limit theorem assumes that the scaling relations are the results by the random merger from a stochastic cloud at higher redshift. In this scenario, the scatter of the scaling relations has to be larger at higher redshift. However, the observed scatter of our high-$z$ sample do not present this feature. In fact, the obtained intrinsic scatter is only $\sim0.13$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}. Of course, the intrinsic scatter of our high-$z$ sample could be underestimated, since manually selected sample avoids the spreading of the properties and decrease the value of the scatter. Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), result in an overestimating of the error-budget and thus underestimating of intrinsic scatter. Still, even we do not take the uncertainties into account to calculate the scatter, the obtained value is $0.25$~dex, which is not larger than the local relations. Thus, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.

Between the MBII and SAM models, they all demonstrate an excellent agreement to the observed data; however, they adopted very different assumptions, recipes, and initial conditions. From another perspective to understand this agreement, there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution, so that more massive BHs are linked to more massive galaxies with some intrinsic scatter. Once the selection function is well defined, the tight correlations would show up along with the selected sample.

@@

\textbf{Imaging data, decomposition and inference of host properties.} 
%1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets, to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman). We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642. To mitigate the contamination from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.

To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting. To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile. We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the library. Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF. We adopt the result from the top-eight PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.

21/32 images in the COSMOS survey also have imaging data in the ACS/F814W with drizzled pixel scale as 0\farcs03, providing us the multi-band information. We decompose the AGN image in the ACS band to obtain the color of the host. We find that the 1Gyr template would well match their color from which we estimate the rest-frame R band luminosity and stellar mass. A Salpeter initial mass function is employed consistently to the observed and simulated sample.

@@

\textbf{Linear fitting and scatter comparison}.  
%How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
To quantitatively understand the consistency between the simulated scaling relations and the observing ones, we use linear fittings and compare their result. Since our selection window has hard cut on the \mbh\ value and the scatter on the host galaxies' properties are larger, we thus fit the host's properties as a function of \mbh. We adopt the {\sc Scipy} package to estimate the best-fit line and its 1-sigma region for the simulated sample. We use the sample slope value to fit for the observations. The comparing results are showing in Figure~\ref{fig:MBII_comp}. To estimate the scatter of the sample, we plot the histogram of the offset value of the sample that deviated from their best-fit. For MBII model, the result are shown in Figure~\ref{fig:offset_comp}. We perform the KS test between the simulation sample and observation sample, and find the p-value are $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations. Considering that the compared simulation sample have the same uncertainty level with same selection effect, we expect they have the same intrinsic scatter level. We adopt {\sc Linmux} to estimate the intrinsic scatter from the overall sample and obtain its value value is $0.25$~dex.

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} &
\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} \\
\end{tabular}
\caption{The histogram comparison of the scatter of the sample offset to its best-fit relation. The standard derivations are identically equal to $0.3$~dex for both HST sample and MBII sample on both sides.
}
\label{fig:offset_comp}
\end{figure*}

@@

\begin{addendum}
 \item[Acknowledgements] 
%X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).

%
\item[Correspondence] %Correspondence and requests for materials should be addressed to Xuheng Ding ~(email:dxh@astro.ucla.edu).
\item[Author Contributions] xxx measure xxx, xxx extract the simulation from xx.
\end{addendum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Additional information}
\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
%The data reduction package used to process the SAMI data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr. To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M. Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}. For the adaptive LOESS smoothing, we use the code from M. Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess

@@

>>>>

\begin{abstract}
Supermassive black holes (BH) harbor at the center of galaxies with their masses (\mbh) correlated to the properties of the host galaxies, including absolute magnitude ($Mag$) and stellar mass (\mstar) known as scaling relations (i.e., \mbh-\lhost, \mbh-\mstar). 
 %Observational results have indicated evidence that this correlation evolves with cosmic time, suggesting a scenario that the BH growth predates their host. In theory, positive evolution of BH is also predicted by several simulation projects independently.
So far, the simulations have reproduced the relations which have a good agreement to the observational sample from local to intermediate redshift ($z<1$). It is crucial to extend this study to higher redshift ($z>1$), where the predicted relations are more sensitive to the initial assumptions and any inconsistency would help to pinpoint the incorrect ones.
To this end, we use a sample of 32 X-ray-selected broad-line (type-1) AGNs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) to make a direct comparison to the predicted sample by two independent state-of-the-art simulation projects: MassiveBlack-II (MBII) and semi-analytic models (SAMs). We adopt \hst\ to take images of the 32 AGNs in multi-bands and deriving the trustworthy stellar mass and use the reliable broad \halpha\ emission lines by Subaru/FMOS to estimate the \mbh. Taking the measurement uncertainty and selection bias into account, %by adopting the same selection function to choose the simulating sample,
we find that both models agree well with the data, \ding{However...} in terms of the central distribution and scatters. Considering the two models use very different recipes, their agreements to the data indicate the existence of a causal connection between BH and the host galaxy, which could not be explained by purely a stochastic process. The intrinsic scatter of our high-$z$ sample is close to simulations and local ones, which is against the central limit theorem. To some extend, our result attests that there is a physical connection induces an ordering so that the more massive black holes are linked to the more massive masses.

@@

% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
To extend the comparison to the simulation models to higher redshift, we collected a sample of 32 \hst-observed AGN systems at redshift range $1.2<z<1.7$ from three X-ray coverage fields, including COSMOS~\cite{Civano2016}, (E)-CDFS-S~\cite{Lehmer2005, Xue2011}, and SXDS~\cite{Ueda2008}. The redshift range of our targets is chosen to be high enough ($z>1$) to detect the existence of the evolution offsets and make the comparison to the models, while low enough ($z<2$) to limit the effect of surface brightness dimming. We selected our AGN sample in a well-defined window as in Figure~\ref{fig:AGN_select}, based on the \mbh\ and Eddington ratio \ding{Do we plot figure1 again, or cite to the QSO I paper?}. As shown, the \mbh\ are well below the knee of the BH mass distribution to avoid strong selection bias and the Eddington ratio are mostly above $0.1$ to ensure the homogeneity.

@@

\begin{figure}[t]
\includegraphics[width=0.9\linewidth]{AGN_selection.pdf}
\caption{The selection for the 32 AGN sample. The top and right panels are the BH mass function and Eddington ratio function. \ding{More descriptions needed if Figure1 is finally decided to shown.}
}
\label{fig:AGN_select}
\end{figure}

To make the comparison, we adopt two independent simulation projects, including MassiveBlack-II (MBII)~\cite{Khandai2015} and semi-analytic models (SAM)~\cite{Menci2014}. These two models are based on independent model strategies, i.e., hydrodynamic simulation for MBII and semi-analytic model for SAM, respectively. The MassiveBlack-II (MBII) simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the simulating objects to evolve independently; the high enough mass and spatial resolution meet the requirements for the object details. On the theoretical side, aimed, high-resolution N-body simulations can study specific galaxy systems. However, understanding the mechanism of the scaling relation requires an analytical description of such processes to be implemented into existing semi-analytic models, such as SAM. In previous works~\cite{Menci2014, Menci2016}[ref], MBII and SAM have made successful predictions. We refer the interested readers to these works for more details.

%\section*{Results}
%Selection effect into account
To make comparison by the MBII project, we collect a sample of simulated AGNs at $z=1.5$ and compare their predicted scaling relations to the observed ones. To ensure a fair comparison, we take the measurement uncertainty and the selection effect into account with the following process. First, we inject the random noise to the simulated sample to mimic the scattering effect that caused by the uncertainty. The assumed uncertainty levels are comparable to the realistic ones, i.e., $\Delta$\mbh =0.4~dex, $\Delta$\mr=0.3~dex, $\Delta$\mstar=0.17~dex and $\Delta L_{\rm bol}$=0.03~dex, respectively. We then select the sample that falls into the same selection window, as shown in Figure~\ref{fig:selectfunc}. We investigated the predicted scaling relations, including \mbh-\mr\ and \mbh-\mstar, and compared them to the observational constraints, as shown in Figure~\ref{fig:MBII_comp}. From a quick glimpse, one can see that the samples are overlapped with each other, showing a sign of agreement. To quantify the level of agreement, we perform the linear regression to fit the simulated relations and estimate the best-fit and 1$-\sigma$ confidence interval. We use the same slope value to fit the best intercept value for the observed sample. We find that for the \mbh-\mr\ relation, the linear fitting results are almost identical, with $0.06$~dex mismatch. For the \mbh-\mstar\ relations, the mismatch ($0.15$~dex) is small and far below 1$-\sigma$ level. We also compare the sample by their scatter. Calculating the standard derivation of the residual, we find the simulations and the observations have the same scatter value $0.3$~dex. Considering that the simulated samples have the same uncertainty and the selection effect, we expect the intrinsic scatter of the scaling relations are similar, which it $0.25$~dex (see METHODS).

\begin{figure}[t]
\includegraphics[width=1.0\linewidth]{MBII_selectfunc.pdf}
\caption{The selection window as adopted for selecting the MBII simulated sample. The yellow background clouds shows the overall sample at $z=1.5$. We add the random uncertainty to the simulation and select the ones located in the selection window (i.e. red region). The yellow dots are the observed sample.}
\label{fig:selectfunc}
\end{figure}
%comparison to simulation (flux ratio also)

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.5\linewidth]{MBII_ML.pdf} &
\includegraphics[width=0.5\linewidth]{MBII_MM.pdf} \\
\end{tabular}
\caption{  In the left and right panel, we present the \mbh-\mr\ and \mbh-\mstar\ correlation between the observed scaling relations (green dots) and the predicted samples (red dots) by the MBII simulation, respectively. The MBII predicted sample are treated to have the same uncertainty and selection effect as the observational ones. The red line is the best-fit result for the simulated sample, with colored region indicating the $1-\sigma$ confidence interval. We use the same slope value to fit for observed sample and the green line shows the best-fit result. The yellow grids in the background are the overall sample that predicted in the MBII simulation.  %{\bf For the right panel, I currently adopt a 3 Gyrs template for the HST sample...}
}
\label{fig:MBII_comp}
\end{figure*}

We also make comparisons of our observed scaling relations to the predictions by SAM model. We consider the sample at $z=1.5$ epoch for two sample sets, including the overall sample and the selected sample. Rather than use N-body simulation to produce individual galaxies, the SAM model use the density clouds to describe the possibility of the samples, as shown in Figure~\ref{fig:SAM_comp}. We find that considering the selecting effect, the direct prediction by SAM is well matched to the observed relations.
%We do not estimate the scatter for SAM model, but visually see that the observed relations are mostly located on top of the hot cloud, showing that the observed scatter should not be larger than the model one. \ding{This is not right yet. But if consider the scatter in the same way, the SAM have large scatter?}
However this is not a proper comparisons yet, since this direct comparison does not include the scattering effect by the measurement uncertainty. To make a valid comparison, we generate a random the overall sample for SAM based on the possibility distribution. Then, same as MBII's case, we inject the random uncertainty to the sample to take the uncertainty effect into account and select the sample the selection window. The resulting comparisons are shown in Figure~\ref{fig:SAM_comp_withnoise}. We find that the best-fit result by the SAM model are well matched to the observation. However, the horizontal scatter of the SAM model are overwhelmingly larger. This larger scatter is a combination result by the SAM distribution, uncertainty and selection effect.

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 24mm 0mm, clip, width=0.45\linewidth]{SAM_ML.pdf} &
\includegraphics[trim = 30.5mm 0mm 0mm 0mm, clip, width=0.45\linewidth]{SAM_MMstar.pdf} \\
\end{tabular}
\caption{Similar to the Figure~\ref{fig:MBII_comp}, but for a direct comparison to the observation using SAM's model. The blue background contours show the possibility distribution for the overall sample, and the red contours indicate the distributions after considering the selecting effect. We presented our observational data as yellow dots. Note that this comparison has not taken the measurement uncertainties into account yet. 
}
\label{fig:SAM_comp}
\end{figure*}

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.45\linewidth]{SAM_ML_consider_nois.pdf} &
\includegraphics[width=0.45\linewidth]{SAM_MM_consider_nois.pdf} \\
\end{tabular}
\caption{Same as the Figure~\ref{fig:MBII_comp}, but for the SAM models.}
\label{fig:SAM_comp_withnoise}
\end{figure*}

To test if any unexpected selection effects exist, we compare the distribution of the host-total flux ratio among these three samples. For the observed sample, we calculate the flux ratio at the imaging band, i.e., \hst/WFC3. For the simulated sample, we consider the AGN bolometric correction~\cite{Elvis1994} to estimate the AGN light flux at WFC3/F125W band. We compare their host-total flux histogram distribution in Figure~\ref{fig:comp_hist} and see that the three samples are well matched each other. The median values for the flux ratio distribution of the observed, MBII, SAM sample are $37.3\%$, $32.3\%$, and $42.8\%$, respectively. We perform the Kolmogorov-Smirnov (KS) test the inferred p-values are 0.34 (for observed -- MBII) and 0.14 (for observed -- SAM), respectively. This result indicates the three samples have similar host-to-total light distribution.

@@

Without any physical mechanisms, the central limit theorem assumes that the scaling relations are the results by the random merger from a stochastic cloud at higher redshift. In this scenario, the scatter of the scaling relations has to be larger with the increasing of redshift. However, the observed scatter of our high-$z$ sample do not present this feature. In fact, our inferred intrinsic scatter of the observed sample is only $\sim0.25$~dex, which is no more than the typical scatter at local relations in the literature ($\sim0.35$~dex)~\cite{Kormendy13, Gul++09}. Of course, the intrinsic scatter of our high-$z$ sample could be inaccurate which, 
since we use the MBII overall sample as proxy to estimate this value.
Also, the observed \mbh\ are estimated using the robust \halpha\ line, which could have lower uncertainties level than expected (i.e., $\Delta$\mbh$<0.4$~dex), result in an overestimating of the error-budget and thus underestimating of intrinsic scatter. Still, the evidence of the low scatter in our measurements is likely to be true, which is against the central limit theorem and suggests that the physical mechanisms between the SMBH and its host galaxy are likely to exist.

The MBII model and SAM model both demonstrate an excellent agreement to the observed data; however, they adopted very different assumptions, recipes, and initial conditions. From another perspective to understand this agreement, there has to be a causal link between SMBH and its host galaxy to generate an ordering during their evolution, so that more massive BHs are linked to more massive galaxies with some intrinsic scatter. Once the selection function is well defined, the tight correlations would show up along with the selected sample.

@@

\textbf{Imaging data, decomposition and inference of host properties.} 
%1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets, to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman). We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642. To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.

To address the bias which might be raised by the unknown PSF, we manually collect the isolated-unsaturated PSF-stars from the 32 observed fields, to assemble a PSF library for the fitting. To decompose each AGN image, we assume the unresolved active nuclei as the scaled point source and the host galaxy as the \sersic\ profile. We adopt imaging modeling tool \lenstronomy\cite{lenstronomy} to simultaneously fit their 2-D flux distribution, taking each PSF one by one from the library. Based on the reduced $\chi^2$, we are capable of evaluating the performance of each PSF. We adopt the result from the top-ranked-eight PSFs and infer the host property, including flux, \reff, \sersic\ index, using a weighted arithmetic mean.

21/32 images in the COSMOS survey also have imaging data in the ACS/F814W with drizzled pixel scale as 0\farcs03, providing us the multi-band information. We decompose the AGN image in the ACS band to obtain the color of the host. We find that the 1~Gyr template could well match their color from which we estimate the rest-frame R band luminosity and stellar mass. A Salpeter initial mass function is employed consistently to the observed and simulated sample.

@@

\textbf{Linear fitting and scatter comparison}.  
%How the fitting is done. The comparing of the histogram and the KS test. The scatter. Figures.
To quantitatively compare the scaling relations between the simulations and the observations, we use linear line to fit their relations and compare the result. Our selection window has a hard cut on the \mbh\ value (vertical direction), and thus the scatter on the host galaxies' properties are larger (horizontal direction). Thus, we fit the host's properties (i.e. \mr\ and \mstar) as a function of \mbh. We adopt the {\sc Scipy} package to estimate the best-fit line and $1-\sigma$ confidence interval for the simulated sample, and use the sample slope value to fit for the observations. The comparing results are showing in Figure~\ref{fig:MBII_comp} and~\ref{fig:SAM_comp_withnoise}. To estimate the scatter of the sample, we plot the histogram of the residual value, which is the deviation of sample to their best-fit. The result are presented in Figure~\ref{fig:offset_comp}. We find the standard derivation for observed and MBII sample are both equal to $\sim0.3$~dex and for SAM the value is $\sim0.7$~dex.  We perform the KS test between observed and MBII sample and infer the p-value as $\sim0.3$ for both \mbh-\mr\ and \mbh-\mstar\ relations. Compared to the observational constraints, the MBII sample is processed to have the same uncertainty level and selected by the same selection function; thus we expect the MBII sample and the observational sample have the same intrinsic scatter level. We adopt the python package {\sc Linmix} and estimate this intrinsic scatter using the MBII overall sample, result in $0.25$~dex.

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.45\linewidth]{comp_scatter_ML.pdf} &
\includegraphics[width=0.45\linewidth]{comp_scatter_MM.pdf} \\
\end{tabular}
\caption{The histogram comparison of the scatter using residual value when fit as linear. The standard derivations for these distribution are $\sim0.3$~dex, $\sim0.3$~dex and $\sim0.7$~dex for observed sample, MBII sample and SAM sample, respectively. Compared to the observation and MBII, the horizontal scatters are much larger in SAM's prediction. 
}
\label{fig:offset_comp}
\end{figure*}

@@

\begin{addendum}
 \item[Acknowledgements] 
Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. These observations are associated with programs \#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555. The authors fully appreciate input from Simon Birrer, Matthew A. Malkan. XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT. JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan. A.S. is supported by the EACOA fellowship.

%
\item[Author Contributions] X.D. carried out the HST data analysis, led the comparison to the simulating models and was the principal author of the paper. T.T. and J.S. designed the HST project and selected the AGN sample. A.B. and T.D. ran the MBII simulation and provide the simulation data. N.M. ran the SAM model and provide and the SAM data. X.D, T.T, J.S., A.B., T.D., and N.M. interpreted the result.

\end{addendum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Additional information}
\textbf{Code availability.} The \lenstronomy, which is used to decompose the AGN image  
%The data reduction package used to process the SAM data is available at http://ascl.net/1407.006, and makes use of 2dfdr: http://www.aao.gov.au/science/software/2dfdr. To derive the stellar kinematic parameters and the lick absorption line strengths, we use the publicly available penalised pixel-fitting (pPXF) code from M. Capppellari: {http://www-astro.physics.ox.ac.uk/~mxc/software/\#ppxf}. For the adaptive LOESS smoothing, we use the code from M. Cappellari obtained from: http://www-astro.physics.ox.ac.uk/~mxc/software/\#loess

@@

\textbf{Correspondence and requests for materials} should be addressed to X.D.~(email:dxh@astro.ucla.edu).
